---
title: "Four Parameters: Categorical"
author: "Ronit Dash"
format: html
execute: 
  echo: false
---

```{r}
#| label: setup
#| message: false
library(primer.data)
library(tidyverse)
library(brms)
library(tidybayes)
library(gtsummary)
```

```{r}
#| label: model
#| cache: true
fit_nes <- brm(formula = pres_vote ~ sex, 
data = nes_92, 
family = categorical(), 
silent = 2, refresh = 0, 
seed = 76)
ndata <- tibble(sex = c("Female", "Male"))
```

```{r}
#| label: cleaning
#| message: false
nes_92 <- nes |> 
  filter(year == 1992) |>
  select(pres_vote, sex) |>
  drop_na() |> 
  mutate(pres_vote = case_when(
    pres_vote == "Democrat" ~ "Clinton",
    pres_vote == "Republican" ~ "Bush",
    pres_vote == "Third Party" ~ "Perot"
  ))
```

```{r}
#| label: plot
fit_nes |> add_epred_draws(newdata = ndata) |> 
select(sex, .category, .epred) |> ggplot(aes(x = .epred, fill = sex)) +
geom_histogram(bins = 100) + facet_grid(~.category) + 
scale_x_continuous(breaks  = c(0.05, 0.3, 0.6), labels = scales::percent_format()) +
labs(title = "Posterior for Expected Probability of Candidate Support Among Women",
subtitle  = "Women are most likely to support Clinton", 
x = "Posterior Probability of Expected Vote Probability", 
y = "Count")
```

We are analyzing a dataset from the American National Election Studies to determine if sex was a factor in voting for the 1992 presidential election. One problem is that the sample is not random enough to accurately represent the population. We made a multinomial logistic regression model to develop approximate intercepts for the votes each candidate get. In our model, women are more likely to support Clinton. Women are around 53% likely to support Clinton, but it could be around 48% or 58%

\begin{aligned}
\rho_{clinton} &=& \frac{e^{\beta_{0, clinton} + \beta_{1, clinton} male}}{1 + e^{\beta_{0, clinton} + \beta_{1, clinton} male}}\\
\rho_{perot} &=& \frac{e^{\beta_{0, perot} + \beta_{1, perot} male}}{1 + e^{\beta_{0, perot} + \beta_{1, perot} male}}\\
\rho_{bush}  &=& 1 - \rho_{clinton} - \rho_{perot}
\end{aligned}


```{r}
#| label: table
tbl_regression(fit_nes)
```



